\documentclass{article}[12pt]
\fontfamily{georgia}

\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amsmath}

\title{CVWO winter assignment Final Writeup}
\author{Albert ZHANG Tongjun}

\begin{document}
\maketitle
\tableofcontents
~\\~\\
This is the final writeup for the CVWO winter assignment.
~\\~\\
In this project, I have built a frontend backend separated project (also my first fullstack project).
The project has three major components: frontend, backend, and database.
The frontend is built with React+Javascript+Typescript. 
The backend is built with golang.
the database is built with mysql.

\section{Manual}
When accessing the website, the user can choose to login with their account, continue as a guest, or register a new account.
~\\~\\
After logging in, the website will display every event related to that account in the current month.
The user can specify a month he/she wants to look at by input the month into the form on the top of the page.
~\\~\\
The user can also focus on one specific day by clicking the ``View by day'' button near the bottom of the page.
~\\~\\
The user can create an event on either the View by day page or the View by month page.



\section{Highlights}
\begin{itemize}
    \item Authentication, both as guests and as registered users
    \item Http requests in ICS format, able to support direct ics file upload with some modification to the frontend
\end{itemize}

\section{Further steps to take}
\begin{itemize}
    \item Add css styling to the project
    \item Add dark mode
    \item Change the view month component to a standard calendar view
    \item Add TLS
\end{itemize}

\end{document}